Appendix: Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-06-25 appendix.qmd
Added True model projections to appendix

@@

>>>>

```{r}
clr_choice <- "#0077A3"
```

@@

```{r}
proj_obj1_true <- read_rds("data/two_nonlinear/two_nonlinear_true_proj_obj1.rds")

two_curvy_proj_true1 <- plot_proj(
  proj_obj = proj_obj1_true,
  point_param = c(0.5, 0.2, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "#000000"), # linewidth, alpha
  plot_limits = c(-0.75, 0.75),
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "a", cex = 1.2) +
  theme(aspect.ratio = 1,
        legend.position = "none")

proj_obj2_true <- read_rds("data/two_nonlinear/two_nonlinear_true_proj_obj2.rds")

two_curvy_proj_true2 <- plot_proj(
  proj_obj = proj_obj2_true,
  point_param = c(0.1, 0.5, clr_choice), # size, alpha, color
  line_param = c(0.5, 0.5, "black"), # linewidth, alpha
  plot_limits = c(-0.5, 0.5),
  axis_text_size = 2,
  is_category = FALSE) +
  interior_annotation(label = "b", cex = 1.2) +
  theme(aspect.ratio = 1)
```

```{r}
#| fig-width: 6
#| fig-height: 3
#| fig-cap: "Two projections of the \\pD{} true model overlaying the data are shown in a, b."

two_curvy_proj_true1 + two_curvy_proj_true2
```
